---
title: 'Step 1: Configure PostreSQL DB'
author: "Neil Kester"
date: "4/24/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      messages = FALSE)
```

# Purpose

These functions are executed once to establish the database and its tables in the Analytic Environment's PostgreSQL instance. They assume the `modSim` database does not already exist.

## Create the `modSim` Database and All Required Tables  

Read in the list of PostgreSQL connection parameters and add the data base name to that list.

```{r fct_low_createModSim}

source("./connectionObjects/pgConnectionObj.R")

pgConnParam[["pgDb"]] <- "modSim2"

fct_low_createModSim <- function(connParamList){
  
  { # Write Query Statements 
    
    createDatabase <- sprintf("CREATE DATABASE \"%s\"",
                              connParamList[["pgDb"]])
    
    createSensorDescriptionTable <- "CREATE TABLE IF NOT EXISTS \"sensorDescription\" (
                   \"sensorId_pkId\" SERIAL PRIMARY KEY,
                   \"sensorId\" TEXT,
                   \"acquireSensorType\" TEXT,
                   \"magnification\" TEXT,
                   \"designPoint\" TEXT)"
    
    createEntityIdToNameTable <- "CREATE TABLE IF NOT EXISTS \"entityIdToName\" (
                   \"entityId_pkId\" SERIAL PRIMARY KEY,
                   \"entityId\" TEXT,
                   \"source\" TEXT,
                   \"designPoint\" TEXT,
                   \"force\" TEXT,
                   \"shortName\" TEXT)"
    
    createSensorToEntityIdTable <- "CREATE TABLE IF NOT EXISTS \"sensorToEntityId\" (
                   \"sensorToEntityId_pkId\" SERIAL PRIMARY KEY,
                   \"sensorId\" TEXT,
                   \"entityId\" TEXT,
                   \"designPoint\" TEXT)"
    
    createUnnestedSensorStateTable <- "CREATE TABLE IF NOT EXISTS \"unnestedSensorState\" (
                   \"id\" TEXT,
                   \"runId\" TEXT,
                   \"runTime\" TEXT,
                   \"designPoint\" TEXT,
                   \"iteration\" TEXT,
                   \"time_ms\" INTEGER,
                   \"time_s\" INTEGER,
                   \"sensorId\" TEXT,
                   \"entityId\" TEXT,
                   \"acquireSensorType\" TEXT,
                   \"magnification\" TEXT,
                   \"source\" TEXT)"
    
    createLosTable <- "CREATE TABLE IF NOT EXISTS \"losState\" (
                   \"id\" TEXT,
                   \"runId\" TEXT,
                   \"runTime\" TEXT,
                   \"designPoint\" TEXT,
                   \"iteration\" TEXT,
                   \"time_ms\" INTEGER,
                   \"time_s\" INTEGER,
                   \"sensorId\" TEXT,
                   \"targetId\" TEXT,
                   \"changeNumber\" INTEGER,
                   \"hasLOS\" BOOLEAN,
                   \"hasLOSUpdateTime\" NUMERIC,
                   \"characteristicDimension\" NUMERIC,
                   \"characteristicDimensionUpdateTime\" NUMERIC,
                   \"background\" TEXT,
                   \"backgroundUpdateTime\" NUMERIC,
                   \"nextUpdateTime\" NUMERIC)"
    
    createSensorAcq <- "CREATE TABLE IF NOT EXISTS \"sensorAcqState\" (
                   \"id\" TEXT,
                   \"runId\" TEXT,
                   \"runTime\" TEXT,
                   \"designPoint\" TEXT,
                   \"iteration\" TEXT,
                   \"time_ms\" INTEGER,
                   \"time_s\" INTEGER,
                   \"receiverId\" TEXT,
                   \"senderId\" TEXT,
                   \"sensorId\" TEXT,
                   \"entityId\" TEXT,
                   \"targetId\" TEXT,
                   \"detectionLevel\" TEXT,
                   \"previousDetectionLevel\" TEXT,
                   \"timeToDetection\" NUMERIC)"
    
  } # close Write Query Statements
  
  { # Connect and send queries
    
    { # Check if the database already exists
      
      pgConn <- DBI::dbConnect(drv = RPostgreSQL::PostgreSQL(),
                               host = connParamList[["pgHost"]],
                               port = connParamList[["pgPort"]],
                               user = connParamList[["pgUser"]],
                               password = connParamList[["pgPass"]])
      
      existingDatabases <- DBI::dbGetQuery(conn = pgConn,
                                           statement = "SELECT * FROM pg_database")$datname
      
      if(connParamList[["pgDb"]] %in% existingDatabases){
        
        message(sprintf("%s Database already exists, moving on to creating tables",
                        connParamList[["pgDb"]]))
        
      }else{
        
        DBI::dbSendQuery(conn = pgConn,
                         statement = createDatabase)
        
        message(sprintf("%s Database created! Moving on to creating tables",
                        connParamList[["pgDb"]]))
        
      } # close else
      
      DBI::dbDisconnect(conn = pgConn)
      
      rm(pgConn)
      
    } # close Check if the database already exists
    
    { # Connect to the supplied database and create tables if they do not exist
      
      pgConn <- DBI::dbConnect(drv = RPostgreSQL::PostgreSQL(),
                               host = connParamList[["pgHost"]],
                               port = connParamList[["pgPort"]],
                               user = connParamList[["pgUser"]],
                               password = connParamList[["pgPass"]],
                               dbname = connParamList[["pgDb"]])
      
      DBI::dbSendQuery(conn = pgConn,
                       statement = createSensorDescriptionTable)
      
      DBI::dbSendQuery(conn = pgConn,
                       statement = createEntityIdToNameTable)
      
      DBI::dbSendQuery(conn = pgConn,
                       statement = createSensorToEntityIdTable)
      
      DBI::dbSendQuery(conn = pgConn,
                       statement = createUnnestedSensorStateTable)
      
      DBI::dbSendQuery(conn = pgConn,
                       statement = createLosTable)
      
      DBI::dbSendQuery(conn = pgConn,
                       statement = createSensorAcq)
      
    } # close Connect to the supplied database and create tables if they do not exist
    
  } # close Connect and send queries
  
  message(sprintf("Complete: The %s database exists and all tables have been created!",
                  connParamList[["pgDb"]]))
  
} # fct_low_createModSim
```  

Execute the `fct_low_createModSim` function:  

```{r}

fct_low_createModSim(connParamList = pgConnParam)

```  
Check  

```{r}

pgConn <- DBI::dbConnect(drv = RPostgreSQL::PostgreSQL(),
                               host = pgConnParam[["pgHost"]],
                               port = pgConnParam[["pgPort"]],
                               user = pgConnParam[["pgUser"]],
                               password = pgConnParam[["pgPass"]],
                               dbname = pgConnParam[["pgDb"]])

DBI::dbListTables(conn = pgConn)  

DBI::dbListFields(conn = pgConn,
                  name = "losState")

```


