---
title: 'Step 2: Query MongoDB, transform data, and write to PostreSQL DB'
author: "Neil Kester"
date: "4/24/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      messages = FALSE)
```

# Purpose

These functions execute the extract, transform, and load (ETL) steps taking the data required to support analysis from the simulation's MongoDB logs, structuring and relating it, and then loading it into a relational database (in this case PostgreSQL) in preparation for later analysis.  

# Low Functions  

## Sensor to Entity Mapping  

This is already implemented in my `{modSim}` package.

**Work to do: Confirm `SensorDescription`, `EntityIdToName`, and `SensorToEntityId` does not need to be split out by iteration. I think not**

**__Note__: This query should not include an iteration filter. Ideally, this is used once per design point.**

```{r fct_low_etlSensorToEntityMappingTables}

source("./connectionObjects/entityMappingConnectionObj.R")

fct_low_etlSensorToEntityMappingTables <- function(mongoConnParam,pgConnParam){
  
  requireNamespace(package = "magrittr")
  
  { # Extract ----
    
    { # Query MongoDb and unnest information about sensors and entities ----
      
      message("Extracting data from MongoDB")
      
      entitySensorMapping <- modSim::mapSensorsAndEntities(mongoUri = mongoConnParam[["mongoUri"]],
                                                           mongoDb = mongoConnParam[["mongoDb"]],
                                                           mongoCollection = mongoConnParam[["collection"]],
                                                           mongoFields = mongoConnParam[["fields"]],
                                                           mongoQuery = mongoConnParam[["query"]])
      
      metaData <- entitySensorMapping$UnnestedSensorState %>%
        dplyr::distinct(.data = .,
                        runId,
                        designPoint,
                        iteration)
      
    } # close Query MongoDb and unnest information about sensors and entities section
    
  } # close Extract section
  
  { # Transform and Load ----
    
    { # sensorDescription ----
      
      message("Transforming and loading sensorDescription data.")
      
      entitySensorMapping$SensorDescription <- entitySensorMapping$SensorDescription %>%
        dplyr::mutate(.data = .,
                      designPoint = dplyr::distinct(metaData,
                                                    designPoint)[[1]],
                      sensorId_pkId = NA)
      
      query_sensorDescription <- fillTableQuery(data = entitySensorMapping$SensorDescription,
                                                tableName = paste0("\"sensorDescription\" (",
                                                                   paste0("\"",
                                                                          names(entitySensorMapping$SensorDescription),
                                                                          "\"",
                                                                          collapse = ","),
                                                                   ")"))
      
      #> This is required because pg uses the unquoted `DEFAULT` for its auto-incrementing columns.
      query_sensorDescription <- stringr::str_replace_all(string = query_sensorDescription,
                                                          pattern = "NULL",
                                                          replacement = "DEFAULT")
      
      sendPgFillTableQuery(query = query_sensorDescription,
                           host = pgConnParam[["pgHost"]],
                           port = pgConnParam[["pgPort"]],
                           user = pgConnParam[["pgUser"]],
                           password = pgConnParam[["pgPass"]],
                           dbname = pgConnParam[["pgDb"]])
      
      rm(query_sensorDescription)
      
    } # close sensorDescription section
    
    { # entityIdToName ----
      
      message("Transforming and loading entityIdToName data.")
      
      entitySensorMapping$EntityIdToName <- entitySensorMapping$EntityIdToName %>%
        dplyr::mutate(.data = .,
                      designPoint = dplyr::distinct(metaData,
                                                    designPoint)[[1]],
                      force = dplyr::case_when(
                        stringr::str_detect(string = source,
                                            pattern = "^(?i)(blueforce)") ~ "BLUEFORCE",
                        stringr::str_detect(string = source,
                                            pattern = "^(?i)(redforce)") ~ "REDFORCE",
                        TRUE ~ "OTHER"
                      ),
                      shortName = stringr::str_extract(string = source,
                                                       pattern = "[^/]*$"),
                      entityId_pkId = NA)
      
      query_entityIdToName <- fillTableQuery(data = entitySensorMapping$EntityIdToName,
                                             tableName = paste0("\"entityIdToName\" (",
                                                                paste0("\"",
                                                                       names(entitySensorMapping$EntityIdToName),
                                                                       "\"",
                                                                       collapse = ","),
                                                                ")"))
      
      #> This is required because pg uses the unquoted `DEFAULT` for its auto-incrementing columns.
      query_entityIdToName <- stringr::str_replace_all(string = query_entityIdToName,
                                                       pattern = "NULL",
                                                       replacement = "DEFAULT")
      
      sendPgFillTableQuery(query = query_entityIdToName,
                           host = pgConnParam[["pgHost"]],
                           port = pgConnParam[["pgPort"]],
                           user = pgConnParam[["pgUser"]],
                           password = pgConnParam[["pgPass"]],
                           dbname = pgConnParam[["pgDb"]])
      
      rm(query_entityIdToName)
      
    } # close entityIdToName section
    
    { # sensorToEntityId ---- 
      
      message("Transforming and loading sensorToEntityId data.")
      
      entitySensorMapping$SensorToEntityId <- entitySensorMapping$SensorToEntityId %>%
        dplyr::mutate(.data = .,
                      designPoint = dplyr::distinct(metaData,
                                                    designPoint)[[1]],
                      sensorToEntityId_pkId = NA)
      
      query_sensorToEntityId <- fillTableQuery(data = entitySensorMapping$SensorToEntityId,
                                               tableName = paste0("\"sensorToEntityId\" (",
                                                                  paste0("\"",
                                                                         names(entitySensorMapping$SensorToEntityId),
                                                                         "\"",
                                                                         collapse = ","),
                                                                  ")"))
      
      #> This is required because pg uses the unquoted `DEFAULT` for its auto-incrementing columns.
      query_sensorToEntityId <- stringr::str_replace_all(string = query_sensorToEntityId,
                                                         pattern = "NULL",
                                                         replacement = "DEFAULT")
      
      sendPgFillTableQuery(query = query_sensorToEntityId,
                           host = pgConnParam[["pgHost"]],
                           port = pgConnParam[["pgPort"]],
                           user = pgConnParam[["pgUser"]],
                           password = pgConnParam[["pgPass"]],
                           dbname = pgConnParam[["pgDb"]])
      
      rm(query_sensorToEntityId)
      
    } # close sensorToEntityId section
    
    { # unnestedSensorState ----
      
      message("Transforming and loading unnestedSensorState data.")
      
      #> This is the full set of un-nested data from the original query. While not truly "raw", this could be considered the original data set.
      
      entitySensorMapping$UnnestedSensorState <- entitySensorMapping$UnnestedSensorState %>%
        dplyr::rename(.data = .,
                      "id" = "_id",
                      "time_ms" = "time")
      
      query_unnestedSensorState <- fillTableQuery(data = entitySensorMapping$UnnestedSensorState,
                                                  tableName = paste0("\"unnestedSensorState\" (",
                                                                     paste0("\"",
                                                                            names(entitySensorMapping$UnnestedSensorState),
                                                                            "\"",
                                                                            collapse = ","),
                                                                     ")"))
      
      sendPgFillTableQuery(query = query_unnestedSensorState,
                           host = pgConnParam[["pgHost"]],
                           port = pgConnParam[["pgPort"]],
                           user = pgConnParam[["pgUser"]],
                           password = pgConnParam[["pgPass"]],
                           dbname = pgConnParam[["pgDb"]])
      
      rm(query_unnestedSensorState)
      
    } # close unnestedSensorState section
    
  } # close Transform and Load section
  
} # close fct_low_etlSensorToEntityMappingTables

```

```{r test_fct_low_etlSensorToEntityMappingTables}

fct_low_etlSensorToEntityMappingTables(mongoConnParam = mongoConnParam,
                                       pgConnParam = pgConnParam)

```  


## Line of Sight Tables  

This table describes when a sensor target has Line of Sight (LOS). This does not mean they have acquired each other but rather that their line of sight is not obstructed. 

```{r fct_low_etlLosData}

source("./connectionObjects/hasLosConnectionObj.R")

fct_low_etlLosData <- function(mongoConnParam,pgConnParam){
  
  requireNamespace(package = "magrittr")
  
  { # Extract ----
    
    message("Extracting data from the MongoDB")
    
    losData <- modSim::mongoUnnest(mongoUri = mongoConnParam[["mongoUri"]],
                                   mongoDb = mongoConnParam[["mongoDb"]],
                                   mongoCollection = mongoConnParam[["collection"]],
                                   mongoFields = mongoConnParam[["fields"]],
                                   mongoQuery = mongoConnParam[["query"]],
                                   unnestCols = "event")
    
  } # close Extract
  
  { # Transform and Load ----
    
    message("Transforming and loading losData")
    
    losData <- losData %>%
      dplyr::rename("id" = "_id",
                    "time_ms" = "time") %>%
      dplyr::mutate(time_s = time_ms/1000,
                    losState_pkId = NA)
    
    query_losData <- fillTableQuery(data = losData,
                                    tableName = paste0("\"losState\" (",
                                                       paste0("\"",
                                                              names(losData),
                                                              "\"",
                                                              collapse = ","),
                                                       ")"))
    
    #> This is required because pg uses the unquoted `DEFAULT` for its auto-incrementing columns.
    query_losData <- stringr::str_replace_all(string = query_losData,
                                              pattern = "NULL",
                                              replacement = "DEFAULT")
    
    sendPgFillTableQuery(query = query_losData,
                         host = pgConnParam[["pgHost"]],
                         port = pgConnParam[["pgPort"]],
                         user = pgConnParam[["pgUser"]],
                         password = pgConnParam[["pgPass"]],
                         dbname = pgConnParam[["pgDb"]])
    
  } # close Transform and Load
  
  rm(query_losData)
  
} # close fct_low_etlLosData

```

```{r test_fct_low_etlLosData}

fct_low_etlLosData(mongoConnParam = mongoConnParam,
                   pgConnParam = pgConnParam)

```
## Sensor Acquisition State Tables  

Unlike the LOS table, this table shows the state of acquisition between each sensor target pair. It also shows the previous acquisition state so we can determine when the acquistion level changes. 

```{r fct_low_etlSensorAcq}

source("./connectionObjects/acqConnectionObj.R")

fct_low_etlSensorAcq <- function(mongoConnParam,pgConnParam){
  
  requireNamespace(package = "magrittr")
  
  { # Extract ----
    
    message("Extracting data from the MongoDB")
    
    sensorAcqData <- modSim::sensorAcquisition(mongoUri = mongoConnParam[["mongoUri"]],
                                               mongoDb = mongoConnParam[["mongoDb"]],
                                               mongoCollection = mongoConnParam[["collection"]],
                                               mongoQuery = mongoConnParam[["query"]],
                                               mongoFields = mongoConnParam[["fields"]],
                                               recursiveUnnests = c("event",
                                                                    "messageData", 
                                                                    "any", 
                                                                    "sensorDetection"))
  
  } # close Extract 
  
  { # Transform and Load ----
    
    message("Transforming and loading losData")
    
    sensorAcqData <- sensorAcqData %>%
      dplyr::rename("id" = "_id",
                    "time_ms" = "time") %>%
      dplyr::mutate(time_s = time_ms/1000,
                    sensorAcqState_pkId = NA)
    
    query_sensorAcqData <- fillTableQuery(data = sensorAcqData,
                                          tableName = paste0("\"sensorAcqState\" (",
                                                             paste0("\"",
                                                                    names(sensorAcqData),
                                                                    "\"",
                                                                    collapse = ","),
                                                             ")"))
    
    #> This is required because pg uses the unquoted `DEFAULT` for its auto-incrementing columns.
    query_sensorAcqData <- stringr::str_replace_all(string = query_sensorAcqData,
                                                    pattern = "NULL",
                                                    replacement = "DEFAULT")
    
    sendPgFillTableQuery(query = query_sensorAcqData,
                         host = pgConnParam[["pgHost"]],
                         port = pgConnParam[["pgPort"]],
                         user = pgConnParam[["pgUser"]],
                         password = pgConnParam[["pgPass"]],
                         dbname = pgConnParam[["pgDb"]])
    
  } # close Transform and Load
  
} # close fct_low_etlSensorAcq

```

```{r test_fct_low_etlSensorAcq}

fct_low_etlSensorAcq(mongoConnParam = mongoConnParam,
                     pgConnParam = pgConnParam)

```


```{r scratch}

pgConn <- DBI::dbConnect(drv = RPostgreSQL::PostgreSQL(),
                         host = pgConnParam[["pgHost"]],
                         port = pgConnParam[["pgPort"]],
                         user = pgConnParam[["pgUser"]],
                         password = pgConnParam[["pgPass"]],
                         dbname = pgConnParam[["pgDb"]])

DBI::dbSendQuery(conn = pgConn,
                 statement = createSensorAcq)

DBI::dbListTables(conn = pgConn)

DBI::dbListFields(conn = pgConn,
                  name = "unnestedSensorState")

DBI::dbGetQuery(conn = pgConn,
               statement = "SELECT * FROM \"sensorAcqState\"")

DBI::dbSendQuery(conn = pgConn,
                 statement = "DROP TABLE \"sensorAcqState\"")

DBI::dbDisconnect(conn = pgConn)

rm(pgConn)

```

