---
title: "Thesis Workflow"
author: "Neil Kester"
date: "4/15/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,messages=FALSE)
```

# Purpose  

# Preparation

## Create a Working PostgreSQL Database  

It is helpful to have a working relational database in which you can store structured data during the analysis process. I am using PostgreSQL over MongoDB because it is a great way to store relational and structured data.  

Previous to this I have created the database `modSim` in the PostgreSQL instance.  

```{r}

source("./connectionObjects/pgConnectionObj.R")

library(RPostgreSQL)

pgDb <- 'modSim'

```

### Create the Required Tables in the Database  

These are the required tables:  

```{r}

pgConn <- DBI::dbConnect(drv = RPostgreSQL::PostgreSQL(),
                         host = pgHost,
                         port = pgPort,
                         user = pgUser,
                         password = pgPass,
                         dbname = pgDb)

createSensorDescriptionTable <- 'CREATE TABLE \"sensorDescription\" (
                   \"sensorId\" TEXT,
                   \"acquireSensorType\" TEXT,
                   \"magnification\" TEXT)'

createEntityIdToNameTable <- 'CREATE TABLE \"entityIdToName\" (
                   \"entityId\" TEXT,
                   \"source\" TEXT)'

createSensorToEntityIdTable <- 'CREATE TABLE \"sensorToEntityId\" (
                   \"sensorId\" TEXT,
                   \"entityId\" TEXT)'

createUnnestedSensorStateTable <- 'CREATE TABLE \"unnestedSensorState\" (
                   \"id\" TEXT,
                   \"runId\" TEXT,
                   \"runTime\" TEXT,
                   \"designPoint\" TEXT,
                   \"iteration\" TEXT,
                   \"time\" INTEGER,
                   \"sensorId\" TEXT,
                   \"entityId\" TEXT,
                   \"acquireSensorType\" TEXT,
                   \"magnification\" TEXT,
                   \"source\" TEXT)'

createLosTable <- 'CREATE TABLE \"losState\" (
                   \"id\" TEXT,
                   \"runId\" TEXT,
                   \"runTime\" TEXT,
                   \"designPoint\" TEXT,
                   \"iteration\" TEXT,
                   \"time\" INTEGER,
                   \"sensorId\" TEXT,
                   \"targetId\" TEXT,
                   \"changeNumber\" INTEGER,
                   \"hasLOS\" BOOLEAN,
                   \"hasLOSUpdateTime\" NUMERIC,
                   \"characteristicDimension\" NUMERIC,
                   \"characteristicDimensionUpdateTime\" NUMERIC,
                   \"background\" TEXT,
                   \"backgroundUpdateTime\" NUMERIC,
                   \"nextUpdateTime\" NUMERIC)'

createSensorAcq <- 'CREATE TABLE \"sensorAcqState\" (
                   \"id\" TEXT,
                   \"runId\" TEXT,
                   \"runTime\" TEXT,
                   \"designPoint\" TEXT,
                   \"iteration\" TEXT,
                   \"time\" INTEGER,
                   \"receiverId\" TEXT,
                   \"senderId\" TEXT,
                   \"sensorId\" TEXT,
                   \"entityId\" TEXT,
                   \"targetId\" TEXT,
                   \"detectionLevel\" TEXT,
                   \"previousDetectionLevel\" TEXT,
                   \"timeToDetection\" NUMERIC)'

RPostgreSQL::dbSendQuery(conn = pgConn,
                         statement = createSensorDescriptionTable)

RPostgreSQL::dbSendQuery(conn = pgConn,
                         statement = createEntityIdToNameTable)

RPostgreSQL::dbSendQuery(conn = pgConn,
                         statement = createSensorToEntityIdTable)

RPostgreSQL::dbSendQuery(conn = pgConn,
                         statement = createUnnestedSensorStateTable)

RPostgreSQL::dbSendQuery(conn = pgConn,
                         statement = createLosTable)

RPostgreSQL::dbSendQuery(conn = pgConn,
                         statement = createSensorAcq)

RPostgreSQL::dbDisconnect(conn = pgConn)

rm(pgConn,
   createSensorDescriptionTable,
   createEntityIdToNameTable,
   createSensorToEntityIdTable,
   createUnnestedSensorStateTable,
   createLosTable,
   createSensorAcq)

```



## Create a Simulation and Entity Table  

First, it is useful to understand information about the sensors and the entities that carried them in the specific "Design Point" and "Iteration" under evaluation. First, lets load the required query and connection object information and then execute the function.   

```{r}

source("./connectionObjects/entityMappingConnectionObj.R")

entitySensorMapping <- modSim::mapSensorsAndEntities(mongoUri = mongoUri,
                              mongoDb = mongoDb,
                              mongoCollection = sensorIDNameCollection,
                              mongoFields = sensorIDNameFields,
                              mongoQuery = sensorIDNameQuery)

#> Clean up the environment
rm(mongoDb,mongoUri,sensorIDNameCollection,sensorIDNameFields,sensorIDNameQuery)
```  


### Sensory Description  

```{r}

entitySensorMapping$SensorDescription

```  

Write this table to the pg database:  

```{r}

query_sensorDescription <- fillTableQuery(data = entitySensorMapping$SensorDescription,tableName = "sensorDescription")


sendPgFillTableQuery(query = query_sensorDescription,
                     host = pgHost,
                     port = pgPort,
                     user = pgUser,
                     password = pgPass,
                     dbname = pgDb)

rm(query_sensorDescription)
```


### Entity ID to Entity Name  

```{r}

entitySensorMapping$EntityIdToName

```

Write this table to the pg database:

```{r}

query_entityIdToName <- fillTableQuery(data = entitySensorMapping$EntityIdToName,tableName = "entityIdToName")

sendPgFillTableQuery(query = query_entityIdToName,
                     host = pgHost,
                     port = pgPort,
                     user = pgUser,
                     password = pgPass,
                     dbname = pgDb)

rm(query_entityIdToName)

```


### Sensor ID to Entity ID  

```{r}

entitySensorMapping$SensorToEntityId

```

Write this table to the pg database:  

```{r}

query_sensorToEntityId <- fillTableQuery(data = entitySensorMapping$SensorToEntityId,tableName = "sensorToEntityId")

sendPgFillTableQuery(query = query_sensorToEntityId,
                     host = pgHost,
                     port = pgPort,
                     user = pgUser,
                     password = pgPass,
                     dbname = pgDb)

rm(query_sensorToEntityId)

```  


### Unnested Sensor State 

This is the full data set produced by the input query.  

```{r}

entitySensorMapping$UnnestedSensorState

```


```{r}

query_unnestedSensorState <- fillTableQuery(data = entitySensorMapping$UnnestedSensorState,
                                            tableName = "unnestedSensorState")

sendPgFillTableQuery(query = query_unnestedSensorState,
                     host = pgHost,
                     port = pgPort,
                     user = pgUser,
                     password = pgPass,
                     dbname = pgDb)

rm(query_unnestedSensorState)

```























## Create a Line of Sight Table  

This table describes when a sensor target has Line of Sight (LOS). This does not mean they have acquired each other but rather that their line of sight is not obstructed.  

```{r}

source("./connectionObjects/hasLosConnectionObj.R")

LosData <- modSim::mongoUnnest(mongoUri = mongoUri,
                               mongoDb = mongoDb,
                               mongoCollection = losMongoCollection,
                               mongoQuery = losMongoQuery,
                               mongoFields = losMongoFields,
                               unnestCols = "event")


#> Clean up the environment
rm(losMongoCollection,losMongoFields,losMongoQuery,mongoDb,mongoUri)
```  

```{r}

LosData

```

Write LosData to the pg database

```{r}
query_losState <- fillTableQuery(data = LosData,
                                 tableName = "losState")

sendPgFillTableQuery(query = query_losState,
                     host = pgHost,
                     port = pgPort,
                     user = pgUser,
                     password = pgPass,
                     dbname = pgDb)

rm(query_losState)
```


## Sensor Target Acquisitions

Unlike the LOS table, this table shows the state of acquisition between each sensor target pair. It also shows the previous acquisition state so we can determine when the acquistion level changes.  

```{r}

source("./connectionObjects/acqConnectionObj.R")

sensorAcq <- modSim::sensorAcquisition(mongoUri = mongoUri,
                          mongoDb = mongoDb,
                          mongoCollection = acqMongoCollection,
                          mongoQuery = acqMongoQuery,
                          mongoFields = acqMongoFields,
                          recursiveUnnests = c("event",
                                               "messageData", 
                                               "any", 
                                               "sensorDetection"))

#> Clean up the environment
rm(acqMongoCollection,acqMongoFields,acqMongoQuery,mongoDb,mongoUri)

sensorAcq
```

```{r}

query_sensorAcqState <- fillTableQuery(data = sensorAcq,
                                       tableName = "sensorAcqState")

sendPgFillTableQuery(query = query_sensorAcqState,
                     host = pgHost,
                     port = pgPort,
                     user = pgUser,
                     password = pgPass,
                     dbname = pgDb)

rm(query_sensorAcqState)

```



# TEMP Nested Tibbles  

## Max Time Value

Take the max from the sensor acquisition and los data frames.

```{r}

pgConn <- DBI::dbConnect(drv = RPostgreSQL::PostgreSQL(),
                         host = pgHost,
                         port = pgPort,
                         user = pgUser,
                         password = pgPass,
                         dbname = pgDb)

maxLosTime <- RPostgreSQL::dbGetQuery(conn = pgConn,
                                      statement = "SELECT max(time) FROM \"losState\"")[[1]]

maxSensorAcqTime <- RPostgreSQL::dbGetQuery(conn = pgConn,
                                      statement = "SELECT max(time) FROM \"sensorAcqState\"")[[1]]

maxTime <- max(maxLosTime,
    maxSensorAcqTime)

RPostgreSQL::dbDisconnect(conn = pgConn)

rm(pgConn,
   maxLosTime,
   maxSensorAcqTime)
```

## Compile All Targets and All Sensors

```{r}

pgConn <- DBI::dbConnect(drv = RPostgreSQL::PostgreSQL(),
                         host = pgHost,
                         port = pgPort,
                         user = pgUser,
                         password = pgPass,
                         dbname = pgDb)

targetsAcq <- RPostgreSQL::dbGetQuery(conn = pgConn,
                                      statement = "SELECT DISTINCT \"targetId\" FROM \"sensorAcqState\"")

targetsLos <- RPostgreSQL::dbGetQuery(conn = pgConn,
                                      statement = "SELECT DISTINCT \"targetId\" FROM \"losState\"")

targets <- dplyr::bind_rows(targetsLos,targetsAcq) %>% dplyr::distinct(targetId)

RPostgreSQL::dbDisconnect(conn = pgConn)

rm(pgConn,
   targetsAcq,
   targetsLos)

```



```{r}

pgConn <- DBI::dbConnect(drv = RPostgreSQL::PostgreSQL(),
                         host = pgHost,
                         port = pgPort,
                         user = pgUser,
                         password = pgPass,
                         dbname = pgDb)

sensors <- RPostgreSQL::dbGetQuery(conn = pgConn,
                                      statement = "SELECT DISTINCT \"sensorId\" FROM \"sensorDescription\"")

RPostgreSQL::dbDisconnect(conn = pgConn)

rm(pgConn)

```






```{r}
### TEMP WORKING AREA
pgConn <- DBI::dbConnect(drv = RPostgreSQL::PostgreSQL(),
                         host = pgHost,
                         port = pgPort,
                         user = pgUser,
                         password = pgPass,
                         dbname = pgDb)

RPostgreSQL::dbListTables(conn = pgConn)

RPostgreSQL::dbListFields(conn = pgConn,name = "sensorDescription")

sensors <- RPostgreSQL::dbGetQuery(conn = pgConn,
                                      statement = "SELECT DISTINCT \"sensorId\" FROM \"sensorDescription\"")

targetsLos <- RPostgreSQL::dbGetQuery(conn = pgConn,
                                      statement = "SELECT DISTINCT \"targetId\" FROM \"losState\"")

targets <- dplyr::bind_rows(targetsLos,targetsAcq) %>% dplyr::distinct(targetId)

RPostgreSQL::dbListFields(conn = pgConn,name = "sensorAcqState")

RPostgreSQL::dbDisconnect(conn = pgConn)

rm(pgConn)
```



## Create a Nested Tibble  

I will now create a nested tibble for each sensor. Each sensor will be an element in a list. Each of those elements will be a tibble where each row is a timestep and the status column is a nested tibble containing all possible targets. As we continue this will be built out to contain the line of sight and acquisition status of each target for that time step by that sensor.

```{r}
# Select a single sensor
sensors[1,][[1]]

# Initialize a list
test <- list()

#> Create a named element in that list for the sensor at hand. Asign to that named 
#>  element a tibble with a row for each timestep and a status list column containing 
#>  all of the targets.
test[[sensors[1,][[1]]]] <- tibble::tibble(time = 0:maxTime,
                                           status = list(targets))


dplyr::glimpse(test)
```

### Specify the Start and Stop time for each state in LOS and Sensor Acquisitions

This rearranges the `LosData` and `sensorAcq` so that each row has a start and stop time for that state.  

```{r}
newLosData <- LosData %>%
  dplyr::select(time,sensorId,targetId,hasLOS) %>%
  dplyr::group_by(sensorId,targetId) %>%
  dplyr::mutate(groups = dplyr::cur_group_id()) %>%
  dplyr::arrange(groups,time) %>%
  dplyr::mutate(nextChange = as.integer(dplyr::lead(time)-1)) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(nextChange = dplyr::case_when(
    is.na(nextChange) ~ max(time),
    TRUE ~ nextChange
  )) %>%
  dplyr::select(time,nextChange,sensorId,targetId,hasLOS)

newSensorAcq <- sensorAcq %>%
  dplyr::select(time,sensorId,targetId,detectionLevel,previousDetectionLevel) %>%
  dplyr::group_by(sensorId,targetId) %>%
  dplyr::mutate(groups = dplyr::cur_group_id()) %>%
  dplyr::arrange(groups,time) %>%
  dplyr::mutate(nextChange = as.integer(dplyr::lead(time)-1)) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(nextChange = dplyr::case_when(
    is.na(nextChange) ~ max(time),
    TRUE ~ nextChange
  ),
  detectionLevel = dplyr::case_when(
    detectionLevel == "SENSOR_NODETECTION" ~ FALSE,
    TRUE ~ TRUE
  ),
  previousDetectionLevel = dplyr::case_when(
    previousDetectionLevel == "SENSOR_NODETECTION" ~ FALSE,
    TRUE ~ TRUE
  )) %>%
  dplyr::select(time,nextChange,sensorId,targetId,detectionLevel,previousDetectionLevel)
```

### Create a function to fill in LOS and Acq data

This function takes an integer representing the current evaluated timestep (`t`), a character of the sensor id (`sen`) and a tibble of targets (`tar`). It returns a tibble with logicals describing if a target could be seen (`hasLOS`) and is currently acquired (`isAcquired`).

```{r}
t <- 14023
losAndAcqData <- function(t,sen,tar){
  message(t)
  tempLos <- newLosData %>%
    dplyr::filter(sensorId == sen,and(time <= t, t <= nextChange)) %>%
    dplyr::select(targetId,hasLOS) %>%
    dplyr::left_join(x = tar,y = .,by = "targetId") %>%
    tidyr::replace_na(list(hasLOS = FALSE))
  
  newSensorAcq %>%
    dplyr::filter(sensorId == sen,and(time <= t, t <= nextChange)) %>%
    dplyr::select(targetId,detectionLevel) %>%
    dplyr::rename("isAcquired"=detectionLevel) %>%
    dplyr::left_join(x = tar,
                     y = .,
                     by = "targetId") %>%
    tidyr::replace_na(list(isAcquired = FALSE)) %>%
    dplyr::left_join(x = .,
                     y = tempLos,
                     by = "targetId")
  
}

tar <- tarList[[1]]

```  

### Apply the function
This needs to be cleaned up so I don't need to call the sensorId.

Filtering where time <= 100 just makes this faster to check.

This creates a list column called `status` by taking the time column, the current sensor's ID, and the targets in the existing status list column and applying the `losAndAcqData()` to it.

```{r}
xyv<-test$`6ef0c641-6693-46ad-943b-203a7792d849` %>% 
  #dplyr::filter(time<=100) %>%
  dplyr::mutate(status = purrr::pmap(.l = list(time,"6ef0c641-6693-46ad-943b-203a7792d849",status),.f = losAndAcqData))
```

Now we have a list describing the status of each target for the specifi sensor-time pair.  

```{r}
xyv[100,]$status[[1]]
```

### Summarise the Status List

To summarize the list column and count the number of targets with LOS and that has been acquired, apply this function.  

```{r}
fun_sum <- function(losCol){
  
  dplyr::summarise(.data = losCol,
                   losCount=sum(hasLOS),
                   acqCount = sum(isAcquired))
  
  
}
```

Apply it in this way.

```{r}
xyv <- xyv %>% 
  dplyr::mutate(time,hasLOS=purrr::map(status,fun_sum)) %>% tidyr::unnest(hasLOS)


```

```{r}
jsonlite::toJSON(xyv[1,2][[1]][[1]])
```


```{r}

sen <- "a15d9d8e-bbbc-4898-9dba-62a9f7e8f615"
tar <- "22d3b6e3-732d-4e69-982e-9431c68d2d05"

function(sen,tar,maxTime){
  
  los <- LosData %>%
    dplyr::filter(sensorId == sen,targetId == tar) %>%
    dplyr::select(time,hasLOS)
  
  acq <- sensorAcq %>%
    dplyr::filter(sensorId == sen,targetId == tar) %>%
    dplyr::select(time,detectionLevel,previousDetectionLevel)
  
  tibble::tibble(time = 0:maxTime) %>%
    dplyr::left_join(x = .,
                     y = los,
                     by = "time") %>%
    dplyr::left_join(x = .,
                     y = acq,
                     by = "time")
    
  
}
```



# Compile Tables  

Using the reference tables created in last section, we will transform them into useful information.

## Sensing Entities  

I only care about Entities (vehicles) that have sensors so I'll drop all entities not in the `SensorToEntityId` table. Then I'll add the description of each sensor and reorder the columns.

```{r}

requireNamespace("magrittr")

humanNameToSensor <- dplyr::left_join(x = entitySensorMapping$EntityIdToName,
                                      y = entitySensorMapping$SensorToEntityId,
                                      by = "entityId") %>%
  dplyr::left_join(x = .,
                   y = entitySensorMapping$SensorDescription,
                   by = "sensorId") %>%
  dplyr::mutate(pltLevelName = stringr::str_extract(string = source,
                                                 pattern = "[^/]*/[^/]*/[^/]*$"),
                shortName =  stringr::str_extract(string = source,
                                                 pattern = "[^/]*$")) %>%
  dplyr::select(shortName,
                pltLevelName,
                acquireSensorType,
                magnification,
                entityId,
                sensorId,
                source)

humanNameToSensor
```

Now that I understand the entities and their sensors, I'll select one entity at a time, starting with `EPBV 90 2`.  

```{r}

entity_epbv_90_2 <- humanNameToSensor %>%
  dplyr::filter(shortName == "EPBV 90 2")

entity_epbv_90_2
```  


# Produce LOS by Sensor - Target Pair

## What Can EPBV 90 2 See Over Time  

First, lets look at what LOS EPBV 90 2 has for each target over time. I'll select only the columns of information I need and filter out all sensors except those on the `EPBV 90 2` platform. 

```{r}

entity_epbv_90_2_los <- LosData %>%
  dplyr::select(sensorId,targetId,time,hasLOS) %>%
  dplyr::filter(sensorId %in% entity_epbv_90_2$sensorId)


entity_epbv_90_2_los
```
That data frame looks good. Finally, I'll filter to see if any of the sensors EVER do not have line of sight with any of the targets.  

```{r}

entity_epbv_90_2_los %>%
    dplyr::filter(!hasLOS)

```
It turns out that various sensors on `EPBV 90 2` do not have line of sight with several targets during this simulation. 

## Start of a LOS Function!

I'll run through all the others sensors and produce "Has LOS" and "Doesn't Have LOS" data frames.  

```{r}

entIds <- dplyr::distinct(humanNameToSensor,entityId)[[1]]

LosResponsesFalse <- list()

LosResponsesTrue <- list()

LosDataSubset <- LosData %>%
  dplyr::select(sensorId,targetId,time,hasLOS)

for(entId in entIds){
  
  testEntity <- dplyr::filter(humanNameToSensor,entityId == entId)
  
  LosResponsesFalse <- LosDataSubset %>%
    dplyr::filter(sensorId %in% testEntity$sensorId) %>%
    dplyr::filter(!hasLOS) %>%
    dplyr::mutate(entityId = entId) %>%
    dplyr::bind_rows(LosResponsesFalse,
                     .)
  
  LosResponsesTrue <- LosDataSubset %>%
    dplyr::filter(sensorId %in% testEntity$sensorId) %>%
    dplyr::filter(hasLOS) %>%
    dplyr::mutate(entityId = entId) %>%
    dplyr::bind_rows(LosResponsesTrue,
                     .)
  
}

LosResponsesFalse <- dplyr::select(LosResponsesFalse, 
              entityId, 
              sensorId,
              targetId,
              time,
              hasLOS)

LosResponsesTrue <- dplyr::select(LosResponsesTrue, 
              entityId, 
              sensorId,
              targetId,
              time,
              hasLOS)

```

Now we have two tidy data frames. One with those observations where the sensor does not have line of sight to a specific target and the second where it does. This data frame contains the entityId, the sensorId, and the targetId so we can get back to human readable names and characteristics of each quickly. It also has the time this event occurred and the `hasLOS` TRUE/FALSE response.

```{r}

LosResponsesFalse

```   

## Summarization

### By Sensor

At this point I will summarize the `LosResponsesTrue` dataframe in two ways. First by counting the number of true LOS events by entityId, sensorId, and time pair. Then I'll do the same by entityId and time pair.  

```{r}

sensorTrueLos <- LosResponsesTrue %>%
  dplyr::group_by(entityId,sensorId,time) %>%
  dplyr::summarise(targetsSensorSees = dplyr::n())

```  

### By Entity  

This is helpful in evaluating a specific sensor but to evaluate the performance of a vehicle or entity, we should summarize but what the vehicle as a whole can see.  

```{r}

entityTrueLos <- LosResponsesTrue %>%
  dplyr::group_by(entityId,time) %>%
  dplyr::summarise(targetsEntitySees = dplyr::n())

entityTrueLos

```

## Plot LOS Count Data!

Now that we have this data, lets plot it. This should be the first layer in our final graph. For readability, I'll filter to only look at "EPBV 90 2"


```{r}

library(ggplot2)

losPlot <- entityTrueLos %>%
  dplyr::left_join(x = .,
                   y = dplyr::select(.data = humanNameToSensor,
                                     entityId,
                                     shortName),
                   by = c("entityId"="entityId")) %>%
  dplyr::filter(shortName == "EPBV 90 2") %>%
  ggplot2::ggplot(data = .) +
  ggplot2::geom_point(mapping = aes(x = time,
                                    y = targetsEntitySees),
                      stroke = 0.15,
                      shape = 4) +
  ggplot2::facet_wrap(~shortName) +
  ggplot2::theme_minimal()

losPlot

```

# Produce Acquisitions by Sensor - Target Pair  

## What **HAS** EPBV 90 2 Seen Over Time  

Similar to the LOS data, lets see what the EPBV 90 2 has sensed over time.  

Note, it appears `senderId`==`sensorId`  


```{r}

entity_epbv_90_2_Acq <- sensorAcq %>%
  dplyr::select(sensorId,
                entityId,
                targetId,
                time,
                detectionLevel,
                previousDetectionLevel,
                timeToDetection) %>%
  dplyr::filter(sensorId %in% entity_epbv_90_2$sensorId)

entity_epbv_90_2_Acq

```  

Now that we have all of the observations for the EPBV 90 2, lets see only those times when targets are acquired:

```{r}
entity_epbv_90_2_Acq_detection <- entity_epbv_90_2_Acq %>%
  dplyr::filter(detectionLevel != "SENSOR_NODETECTION")
```  

```{r}
tempDetected <- entity_epbv_90_2_Acq_detection %>%
  dplyr::left_join(x = .,
                   y = dplyr::distinct(.data = dplyr::select(.data = humanNameToSensor,
                                                             entityId,
                                                             shortName),
                                       entityId,
                                       shortName),
                   by = c("entityId"="entityId")) %>%
  dplyr::select(shortName,
                entityId,
                sensorId,
                targetId,
                time,
                detectionLevel,
                previousDetectionLevel,
                timeToDetection) %>% 
    dplyr::distinct(shortName,entityId,time,targetId) %>%
    dplyr::group_by(shortName,entityId,time) %>%
  dplyr::summarise(targetsEntityAcquires = dplyr::n()) %>%
  dplyr::ungroup()

tempCombined <- entityTrueLos %>%
  dplyr::left_join(x = .,
                   y = dplyr::select(.data = humanNameToSensor,
                                     entityId,
                                     shortName),
                   by = c("entityId"="entityId")) %>%
  dplyr::filter(shortName == "EPBV 90 2") %>%
  dplyr::ungroup() %>%
  dplyr::full_join(x = .,
                   y = dplyr::select(.data = tempDetected,
                                           entityId,
                                           time,
                                           targetsEntityAcquires),
                   by = c("entityId"="entityId","time"="time")) 

tempCombined %>%
  dplyr::distinct(entityId,time,targetsEntitySees,shortName,targetsEntityAcquires) %>%
  dplyr::arrange(time) %>%
  dplyr::mutate(
    targetsEntitySees = dplyr::case_when(
      is.na(targetsEntitySees) ~ dplyr::lag(targetsEntitySees),
      TRUE ~ targetsEntitySees),
    shortName = dplyr::case_when(
      is.na(shortName) ~ dplyr::lag(shortName),
      TRUE ~ shortName),
    targetsEntityAcquires = dplyr::case_when(
    is.na(targetsEntityAcquires) ~ dplyr::lag(targetsEntityAcquires),
    TRUE ~ targetsEntityAcquires)) %>%
  dplyr::arrange(time) %>% 
  ggplot2::ggplot(data = .) +
  ggplot2::geom_point(mapping = aes(x = time,
                                    y = targetsEntitySees),
                      stroke = 0.25,
                      shape = 4,
                      color = "blue") +
  ggplot2::geom_point(mapping = aes(x = time,
                                    y = targetsEntityAcquires),
                      stroke = 0.25,
                      shape = 25,
                      color = "red")


```



```{r}

entitySensorMapping$SensorDescription

entitySensorMapping$EntityIdToName


dplyr::distinct(LosData,time)
```



```{r}

entitySensorMapping$EntityIdToName

```

```{r}

entitySensorMapping$SensorToEntityId

```







